Efficient Data Provenance Analysis for Concurrent Programs

### 2013-11-13 paper.tex
committing after a read through.  I think it's getting there.

\begin{table}
\centering
\small
\begin{tabular}{l | r r }
\multirow{3}{*}{\bf Application} & \multicolumn{2}{c}{\bf \em Pruned } \\
               & \multicolumn{2}{c}{\bf \em Static Local}  \\ 
               & \multicolumn{2}{c}{\bf \em Operations}    \\ \hline

@@

We have discussed bad value origin tracking ~\cite{badapples} throughout this
work and compared directly with that technique in our evaluation.  Bad value
origin tracking is like our work because they store provenance information to
be used for debugging -- a similar goal to ours.  Bad value origin tracking
differs from our work in several ways.  First, their technique only tracks the
provenance of {\em unusable} values -- a fraction of all values in an
execution.  Our work, instead, tracks provenance for any value stored in a
potentially shared memory location, which includes a broader set of provenance
and targets our technique to concurrency debugging.  Second, their technique
does not run with overheads tolerable for performance for C and C++ programs.
They implement their technique for C and C++ programs using Valgrind MemCheck,
which has high runtime overheads.  Our technique has overheads low enough for
production in many cases, especially in server applications.  Third, their
technique does not explicity record thread information with tracked origins.
Our work focuses on concurrency and we include thread information.  As we show
in Section~\ref{sec:eval:debugging} thread information is important for
understanding some bugs.  Fourth, their technique uses bad value piggy-backing
to store origins, we use a shadow memory.

@@

Thin Slicing~\cite{thinslicing}, is a slicing technique that is related to our
work.  Thin Slicing yields the set of statements that computed on or wrote
values that influenced a particular variable's value (the ``seed'').  Thin
Slicing is similar in that its slices provide provenance and it excludes
control information like our work.  Thin Slicing is different in that it has
overheads too high for production and focused on minimizing the size 
of each slice.

>>>>

\begin{table}[htb]
\centering
\small
\begin{tabular}{l | r r }
\multirow{3}{*}{\bf Application} & \multicolumn{2}{c}{\bf \em Pruned } \\
               & \multicolumn{2}{c}{\bf \em Static Local}  \\ 
               & \multicolumn{2}{c}{\bf \em Operations}    \\ \hline

@@

We have discussed bad value origin tracking~\cite{badapples} throughout this
work and compared directly with that technique in our evaluation.  Bad value
origin tracking is like our work because they store provenance information to
be used for debugging -- a similar goal to ours.  Bad value origin tracking
differs from our work in several ways.  First, their technique only tracks the
provenance of {\em unusable} values -- a fraction of all values in an
execution.  Our work, instead, tracks provenance for any value stored in a
potentially shared memory location, which includes a broader set of provenance
and targets our technique to concurrency debugging.  Second, their technique
does not run with overheads tolerable for performance for C and C++ programs.
They implement their technique for C and C++ programs using Valgrind MemCheck,
which has high runtime overheads.  Our technique has overheads low enough for
production in many cases, especially in server applications.  Third, their
technique does not explicity record thread information with tracked origins.
Our work focuses on concurrency and we include thread information.  As we show
in Section~\ref{sec:eval:debugging} thread information is important for
understanding some bugs.  Fourth, their technique uses bad value piggy-backing
to store origins, we use a shadow memory.

@@

Thin Slicing~\cite{thinslicing}, is a slicing technique that is related to our
work.  Thin Slicing yields the set of statements that computed on or wrote
values that influenced a particular variable's value (the ``seed'').  Thin
Slicing is similar in that its slices provide provenance and it excludes
most control information like our work.  Thin Slicing is different in that it has
overheads too high for production and focused on minimizing the size 
of each slice compared to prior slicing techniques.
